---
title: "Code for project"
author: "Charles Alba"
date: "March, 2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,warning=FALSE,message=FALSE, include=FALSE}
library(data.table)
library(rvest)
library(reshape2)
library(jsonlite)
library(stringr)
library(lubridate)
library(geosphere)
library(dplyr)
#install.packages("tidyverse")
#library(tidyverse)
library(rmarkdown)
library(ggplot2)
library(plyr)
library(lsmeans)
library(multcompView)
library(lmtest)
library(nortest)
library(MASS)
library(olsrr)
library(nortest)
library(lsmeans)
library(car)
library(multcompView)
library(lme4)
library(lmerTest)
library(text2vec)
library(pdist)
library(olsrr)
library(MASS)
library(mice)
library(Amelia)
library(AER)
library(bit64)
```

Read csv file
```{r}
imputed_data <- read.csv(file = 'Proj/Volume/Data/processed/covid_and_behavioral.csv')
GHS.index <- read.csv(file = 'Proj/Volume/Data/raw/covid_and_behavioral.csv')
```


obtain the correlation plot
```{r}
c<-subset(imputed_data, select = c( idv, pdi, mas,ivr,ltowvs ,uai))
c<-cor(c)
library(corrplot)
corrplot(c, method="circle", order="hclust", tl.col="black")
```


# Analysis

Apply poisson regression with the entire dataset. 
```{r}
imp_regre<-glm(formula = lambda~pdi+idv+mas+uai+ltowvs+ivr, family = poisson, data=timputed_data , offset=log(population/1000000))
summary(imp_regre)
```


Test for the assumptions 
```{r}
model <- lm(log(lambda) ~ idv, data = timputed_data)
plot(model,1)
dispersiontest(imp_regre)
```



# performing train-test split
```{r}
GHS_data<- read.csv(file='GHS.csv')
timputed_data<-merge(timputed_data, GHS_data, by.x = "location", by.y = "country")
smp_size <- floor(0.7 * nrow(timputed_data))
train_ind <- sample(seq_len(nrow(timputed_data)), size = smp_size)

train <- timputed_data[train_ind, ]
test <- timputed_data[-train_ind, ]
```

Training our model
```{r}
regre<-glm(formula = lambda~pdi+idv+mas+uai+ltowvs+ivr, family = poisson, data=train , offset=log(population/1000000))
summary(regre)
```


Training the GHS model
```{r}
train$neg_ghs<- (train$GHS.index)
regre_GHS<-glm(formula = lambda~(neg_ghs), family = poisson, data=train , offset=log(population/1000000))
summary(regre_GHS)
```


Comparisons between the model (without any basis of direction for the GHS model)
```{r}
actual_behavior = test$lambda
predy_behavior  = predict(regre, newdata=test, interval='prediction')

test$pred<-predy_behavior
RSS = sum((actual_behavior - predy_behavior)^2)
MSE_act=RSS/nrow(test)
```


Comparisons between the models with the directional basis of the GHS model 
```{r}
actual=test$lambda
predy_GHS  = exp(0.4774393-0.0545232*(test$GHS.index)+log(test$population/1000000))
RSS_GHS = sum((actual - predy_GHS)^2)
MSE_GHS=RSS_GHS/nrow(test)
```


```{r}
MSE_GHS-MSE_act #our model is better
```


# Graphs to visualize our model. 

parameter $r_i$

```{r}
timputed_data$r_i<-(timputed_data$total_cases/timputed_data$population)*1000000
logr_i<-log(timputed_data$r_i)
g= ggplot(timputed_data, aes(idv, logr_i, label=location))
```


```{r}
g + geom_jitter()+geom_text(color="green4")+labs(x= "individualism index", y = "log(COVID cases per million population)")+ geom_smooth(method = "lm")
```

```{r}
g= ggplot(timputed_data, aes(pdi, logr_i, label=location))

g + geom_jitter()+geom_text(color="green4")+labs(x= "power distance index", y = "log(COVID cases per million population)")+ geom_smooth(method = "lm")
```

```{r}
g= ggplot(timputed_data, aes(mas, logr_i, label=location))

g + geom_jitter()+geom_text(color="red3")+labs(x= "masculinity index", y = "log(COVID  cases per million population)")+ geom_smooth(method = "lm")
```


```{r}
g= ggplot(timputed_data, aes(uai, logr_i, label=location))

g + geom_jitter()+geom_text(color="green4")+labs(x= "uncertainty avoidance index", y = "log(COVID  cases per million population)")+ geom_smooth(method = "lm")
```


```{r}
g= ggplot(timputed_data, aes(ltowvs, logr_i, label=location))

g + geom_jitter()+geom_text(color="green4")+labs(x= "long-term orientation index", y = "log(COVID  cases per million population)")+ geom_smooth(method = "lm")
```


```{r}
g= ggplot(timputed_data, aes(ivr, logr_i, label=location))

g + geom_jitter()+geom_text(color="green4")+labs(x= "indulgence index", y = "log(COVID  cases per million population)")+ geom_smooth(method = "lm")
```


```{r}
write.csv(timputed_data, file = 'covid_and_behaviorial_data.csv')
```

